Local Group Satellite Distributions in the Illustris Simulation

### 2017-10-06 paper/paper.tex
+1 paragraph LG distributions

\subsection{Distributions in the Local Group}

@@

The lower two panels re-inforce the picture of a highly structured.

>>>>

\subsection{Satellite distributions in the Local Group}

@@

The lower left panel re-inforce the picture of a highly structured
MW. 
It corresponds to the $c/a$ ratio and shows the same trends observed
in for the plane width. 
First, the ratio is lower for the MW than it is for M31; second, the
ratio for the MW is also lower than the expectation for the randomized
sample while the results for M31 is within the expectations from \rand.  
In this case the median value of the \rand\ distributions follow the
$1:1$ line as expected.
The lower right panel does not show any surprises. 
All the distributions from \rank, \boot\ and \rand\ are consistent
both for the MW and M31.
